---
title: "SMCL Coding Club"
output: html_notebook
---

# Overview

When people make reaches they use many signals to determine where their hand is. This includes efferent-based predictions of hand localization as well as afferent proprioceptive signals. Based on context people will rely more on predictions, and efferent signals to determine where their hand is. Here we trained people in the same pertubation with different types of information about the rotation. We test their explicit strategies to gauge if these contexts had effect on learning and then compare active and passive hand localization which respectively do or do not include efferent information. We expect groups with more explicit adaptation to rely on preictions more in their hand localization.

In this experiment, participants adapted to a 30 degree rotation with various kinds of feedback:

1. Regular cursor feedback: "control"
2. Cursorjump feedback, where the cursor is shown at 1/3rd the reach on each training trial: "cursorjump"
3. A group where both the cursor and hand were visible during training: "handview"
4. A group that was explained the rotation before: "instructed"

All reaches were to targets at 45, 90, and 135 degrees.

# Data

There are several kinds of data we could analyze

1. Training reaches
2. No cursor reaches
3. Passive localization
4. Active localization

Both collected in the aligned and rotated phase of the task.

#Setup

get necessary packages:
```{r}
library('remotes')
ip <- installed.packages()
if ('Reach' %in% ip[,'Package']) {
  if (ip[which(ip[,'Package'] == 'Reach'),'Version'] < "2025.02.16") {
    remotes::install_github('thartbm/Reach')
  }
} else {
  remotes::install_github('thartbm/Reach')
}
```

Syn the R environment?

Source project code:

```{r}
# download and handle data:
source('R/data.R')
# scripts for training reaches:
source('R/reaches.R')
```


## Analysis plan

### Training

Did participants learn? Maybe we exclude some. 

Did all groups learn to the same extent?

Did all groups learn equally quickly?

### No-cursors

There were two types of open-loop reaches. With or without strategy. 

In groups with a difference between these two, there is definitely a strategy. 

Perhaps the difference between with and without staretgy no-cusor reaches can be used as a measure of strategy.


### Hand localization 

Is there a difference between active and passive localization? 

Is this different in the different conditions?

# Reach Training

1. Calculate baseline (trials 31 - 45: 5 reaches per target)

## remove outliers

## use more trials to estimate baseline bias 
2. Correct rotated reaches for baseline deviation
3. Plot a learning curve

(4. fit an exponetial to the learning curve)

